### 2012-09-29 doc/prelim/document/chapters/introduction/introduction.tex
adding figure to introduction

\section{Motivation}
\label{sec:motivation}

\subsection{Problems of Interest}
\label{subsec:problems of interest}

@@

\subsection{Multiphysics Methods Advancement}
\label{subsec:methods_advancement}
For some time, the particle transport community has been utilizing
Monte Carlo methods for the solution of transport problems
\citep{lewis_computational_1993}. The partial differential equation
(PDE) community has focused on various deterministic methods for
solutions to linear problems \citep{saad_iterative_2003,
  kelley_iterative_1995}. In between these two areas are a not widely
known small group of stochastic methods for solving sparse linear
systems \citep{forsythe_matrix_1950, hammersley_monte_1964,
  halton_sequential_1962, halton_sequential_1994}. In recent years,
these methods have been further developed for transport problems in
the form of Monte Carlo Synthetic-Acceleration (MCSA)
\citep{evans_residual_2003, evans_monte_2009, evans_monte_2012} but
have yet to be applied to more general sparse linear systems commonly
generated by the computational physics community. Compared to other
methods in this regime, MCSA offers three attractive qualities; (1)
the linear problem operator need not be symmetric or
positive-definite, thereby reducing preconditioning complexity, (2)
the stochastic nature of the solution method provides a natural
solution to the issue of resiliency, and (3) is amenable to
parallelization using modern methods developed by the transport
community \citep{wagner_hybrid_2010}. The developement of MCSA as a
general linear solver and the development of a parallel MCSA method
will be new and unique features of this work, providing a framework
with which other issues such as resiliency may be addressed.

>>>>

\section{Motivation}
\label{sec:motivation}
Predictive modeling and simulation capability requires the combination
of high fidelity models, high performance computing hardware that can
handle the intense compute loads required by these models, and modern
algorithms for solving these problems that leverage this high
performance hardware. For nuclear reactor analysis, this predictive
capability can enable tighter design tolerances for improved thermal
performance and efficiency, higher fuel burnup and therefore reduction
in generated waste, and high confidence in accident scenario
models. The physics that dominate these types of analysis include
neutronics, thermal hydraulics, computational fluid dynamics, and
structural mechanics.

Although solution techniques in each of these individual categories
has advanced over the last few decades and in fact leveraged modern
algorithms and computer architectures, true predictive capability for
engineered systems can only be achieved through a coupled, multiple
physics analysis where the effects of feedback between physics are
modeled. For example, consider the safety analysis of a departure from
nucleate boiling scenario in the subchannel of a nuclear fuel assembly
as shown in Figure~\ref{fig:dnb_example}.
\begin{figure}[htpb!]
  \begin{center}
    \scalebox{1.5}{
      \input{chapters/introduction/dnb_example.pdftex_t} }
  \end{center}
  \caption{\textbf{Multiphysics analysis of departure from nuclear
      boiling.} \textit{A neutronics solution is required to compute
      power generation in the fuel pins, fluid dynamics is required to
      characterize boiling and fluid temperature and density, heat
      transfer is required to compute the fuel and cladding
      temperature, and the nuclear data modified with the temperature
      and density data. Strong coupling among the variables creates a
      nonlinearities.}}
  \label{fig:dnb_example}
\end{figure}
When this event occurs, heat transfer is greatly reduced between the
fuel and the coolant, causing the fuel centerline temperature to
rapidly rise. To characterize this boiling phenomena and how it
affects fuel failure we must consider a neutronics analysis in order
to compute power generation in the fuel pins, fluid dynamics analysis
to characterize coolant boiling, temperature, and density, solid
material heat transfer to characterize fuel and cladding temperature
and heat transfer with the coolant, and nuclear data processing to
characterize how changing material temperatures and densities changes
the cross sections needed for the neutronics calculation. As shown in
Figure~\ref{fig:dnb_example}, many couplings are required among
individual physics components in order to accurately model this
situation with each physics generating and receiving many
responses. Those variables that are very tightly coupled, such as the
temperatures generated by the fluid dynamics and heat transfer
components, will have strong nonlinearities in their behavior and
would therefore benefit from fully consistent nonlinear solution
schemes instead of fixed-point type iterations between
physics\footnote{Fixed-point iterations between physics are commonly
  referred to as Picard iterations.}. Furthermore, the space and time
scales over which these effects occur will also vary greatly.

@@

\subsection{Multiphysics Methods Advancement}
\label{subsec:methods_advancement}
For some time, the particle transport community has been utilizing
Monte Carlo methods for the solution of transport problems
\citep{lewis_computational_1993}. The partial differential equation
(PDE) community has focused on various deterministic methods for
solutions to linear problems \citep{saad_iterative_2003,
  kelley_iterative_1995}. In between these two areas are a not widely
known small group of stochastic methods for solving sparse linear
systems \citep{forsythe_matrix_1950, hammersley_monte_1964,
  halton_sequential_1962, halton_sequential_1994}. In recent years,
these methods have been further developed for transport problems in
the form of Monte Carlo Synthetic-Acceleration (MCSA)
\citep{evans_residual_2003, evans_monte_2009, evans_monte_2012} but
have yet to be applied to more general sparse linear systems commonly
generated by the computational physics community. Compared to other
methods in this regime, MCSA offers three attractive qualities; (1)
the linear problem operator need not be symmetric or
positive-definite, thereby reducing preconditioning complexity, (2)
the stochastic nature of the solution method provides a natural
solution to the issue of resiliency, and (3) is amenable to
parallelization using modern methods developed by the transport
community \citep{wagner_hybrid_2010}. The developement of MCSA as a
general linear solver and the development of a parallel MCSA method
will be new and unique features of this work, providing a framework
with which other issues such as resiliency may be addressed in the
future.
